We present \textsc{Snarc Axiom} (\textsc{Axiom}), a cryptographic payment protocol that achieves
double-spend prevention, full transaction privacy, and fast finality without
maintaining a global transaction ledger as the canonical state repository.
Existing privacy-preserving payment systems, including Zcash and its
predecessors, retain a blockchain as the substrate for nullifier sets and coin
existence records, imposing storage and bandwidth costs that grow linearly with
transaction history---creating long-run pressure toward centralization through
increasing full-node burden.
\textsc{Axiom} replaces the ledger with two compact state objects: a dynamic
RSA accumulator over coin commitments (constant 256~bytes) and a Sparse Merkle
Tree root commitment over the spent nullifier set (constant 32~bytes).
Spent-set growth is captured by this constant-size root and can be
checkpointed and archived without affecting verification.
Transaction validity is established entirely through zero-knowledge proofs;
coin existence is verified via accumulator membership witnesses; and
double-spend prevention follows from the uniqueness of nullifiers derived via a
pseudorandom function.
Global consistency of these two state objects is achieved through a hybrid
finality sublayer combining BFT threshold signatures with VDF-based ordering
beacons, producing finalization certificates in place of ledger entries.
We formalize six cryptographic security properties---correctness,
unforgeability, value conservation, double-spend resistance, anonymity, and
non-malleability---and three distributed-systems properties---safety,
liveness, and atomic state transition---providing proof sketches under standard
assumptions (discrete logarithm, collision resistance, PRF security, RSA
strong assumption, and, where required by the SNARK extractor, a knowledge
assumption standard in pairing-based proof system analyses).
We further present a permissionless committee selection mechanism based on VRF
sortition with stake-weighted admission, and a spam-resistance layer compatible
with both semi-permissioned and fully open deployments.
Concrete instantiation with Groth16 over BLS12-381, RSA-2048 accumulators,
BLS threshold signatures, and ECVRF yields an estimated end-to-end finality of
2--5 seconds and approximately 60~TPS on reference hardware.
