This paper presented \textsc{Axiom}, a cryptographic payment protocol that
achieves double-spend prevention, full transaction privacy, and fast finality
without a global transaction ledger.
The core insight is that blockchain's three roles---canonical ordering, nullifier
tracking, and coin-validity auditing---can be disaggregated.
Coin validity becomes a ZK proof; coin existence becomes an accumulator
membership witness; double-spend prevention becomes a nullifier registry; and
global consistency becomes a BFT finalization certificate.
Together, these replace the ledger with two constant-size state roots and a
thin finality layer.

We formalized this design through nine theorems covering correctness,
unforgeability, value conservation, double-spend resistance, anonymity,
non-malleability, safety, liveness, and atomic state transition.
We extended the model to epoch rotation, permissionless VRF sortition, and a
composable spam-resistance layer, and provided a concrete instantiation with
estimated latency of 2--5~seconds and~${\approx}60$~TPS on reference hardware.

\paragraph{Open problems.}
Four engineering challenges remain for production deployment:
(i)~stake concentration and plutocracy risk in permissionless admission;
(ii)~calibration of spam-resistance parameters across heterogeneous
deployments;
(iii)~the trusted-setup versus performance trade-off in accumulator and proof
system selection; and
(iv)~long-term archive and checkpoint operation at scale.
We leave formal treatment of these to future work.
