\paragraph{Privacy-preserving payments.}
The Zerocash line~\cite{ben2014zerocash} standardized the
nullifier-plus-ZK-proof approach to transaction privacy, and Zcash
Sapling~\cite{zcash2022protocol} industrialized it with production-grade
circuit design and a nullifier note commitment scheme.
\textsc{Axiom}'s cryptographic core shares this lineage but removes the
blockchain substrate entirely.
Groth16~\cite{groth2016size} and PLONK~\cite{gabizon2019plonk} underpin our
``succinct proof, fast verify'' requirements.

\paragraph{Compact-state and ledgerless approaches.}
Utreexo~\cite{dryja2019utreexo} demonstrates that Bitcoin full-node storage
can be dramatically compressed by replacing the UTXO set with a dynamic hash
accumulator and shifting proof storage to users.
\textsc{Axiom} follows the same ``state = compact root'' intuition but targets
a stronger goal: no total-order log of past transactions is maintained at all.
Mimblewimble~\cite{jedusor2016mimblewimble} achieves cut-through compression
via Pedersen commitments while retaining a blockchain; \textsc{Axiom} further
eliminates that requirement.

\paragraph{BFT finality and partial synchrony.}
Our consistency layer is grounded in the partial synchrony model of
Dwork--Lynch--Stockmeyer~\cite{dwork1988consensus}.
PBFT~\cite{castro1999pbft} establishes the quorum-intersection argument that
underpins our \cref{thm:safety,thm:rotation-safety}.
HotStuff-class protocols provide the $O(\Delta)$ liveness bound used in
\cref{thm:liveness}.

\paragraph{VRF-based sortition.}
Algorand~\cite{gilad2017algorand} introduced private VRF sortition for
committee selection in a Byzantine agreement context, achieving unpredictability
without a central coordinator.
\textsc{Axiom} Section~\ref{sec:committee} extends this with stake-weighted
adaptive sizing, epoch rotation compatibility, and a beacon seed chain that
resists grinding (\cref{lem:seed}).
ECVRF is standardized in RFC~9381~\cite{rfc9381}.

\paragraph{Verifiable Delay Functions.}
Pietrzak~\cite{pietrzak2019vdf} and Wesolowski~\cite{wesolowski2019vdf}
independently constructed efficient VDFs; Boneh~et~al.~\cite{boneh2018vdfsurvey}
survey both.
\textsc{Axiom} uses VDFs in two roles: (i) as an ordering beacon to constrain
leader discretion (\cref{sec:consistency}), and (ii) as a temporal barrier
against long-range attacks (\cref{thm:longrange}).
