\subsection{Component Choices}

\paragraph{ZK proof system.}
We instantiate with Groth16~\cite{groth2016size} over BLS12-381 as the default
(smallest proof size, fastest verification).
PLONK~\cite{gabizon2019plonk} is the recommended upgrade path (universal
trusted setup, circuit-agnostic).
STARKs are noted for post-quantum scenarios at the cost of larger proofs
(${\sim}100$~KB).

\paragraph{Accumulator.}
RSA-2048 accumulator with batch witness updates~(Boneh~et~al.~2019).
$H'$ maps to primes via deterministic probable-prime search.
Alternative: class-group accumulator (no trusted setup; 3--5$\times$ slower).

\paragraph{Commitment scheme.}
Pedersen commitments over BLS12-381 $\mathbb{G}_1$:
$\mathsf{Com}(v;\, r) = v \cdot G + r \cdot H$.

\paragraph{PRF and hash.}
$\mathsf{PRF}_s(\rho) = \mathsf{BLAKE3}(s \| \rho)$ (circuit-external);
Poseidon hash inside ZK circuits for efficient constraint generation.

\paragraph{Threshold signature.}
BLS threshold signatures over BLS12-381.
Aggregated signature size: 48~bytes (constant in~$n$).
Verification: 2 pairings $\approx 3$~ms.

\paragraph{VDF.}
Wesolowski VDF~\cite{wesolowski2019vdf} with 2048-bit RSA modular squaring.
$T = 4{,}000$ squarings $\approx 2$~seconds on a single CPU core.
Verification $\approx 5$~ms.

\paragraph{VRF.}
ECVRF over Ed25519 per RFC~9381~\cite{rfc9381}.

\subsection{ZK Circuit Estimate}

\begin{table}[!t]
\centering
\caption{Approximate R1CS constraint counts for relation~$\mathcal{R}$.}
\label{tab:constraints}
\begin{tabular}{lr}
\toprule
\textbf{Constraint source} & \textbf{R1CS constraints} \\
\midrule
Pedersen commitment ($\times 2$) & 500 \\
Poseidon hash ($\times 3$) & 1{,}200 \\
PRF / BLAKE3 (Poseidon substitute) & 800 \\
RSA membership witness verify & 15{,}000 \\
Value range proof & 500 \\
\midrule
\textbf{Total} & $\mathbf{\approx 18{,}000}$ \\
\bottomrule
\end{tabular}
\end{table}

Estimated proving times (Groth16, 18K R1CS):
RTX~4090: $\approx 400$~ms;\quad
RTX~5090: $\approx 200$~ms;\quad
Server FPGA: $\approx 50$~ms.

\subsection{End-to-End Latency}

\[
  T_{\mathit{total}} = \underbrace{T_{\mathit{prove}}}_{\text{200--400 ms}}
  + \underbrace{T_{\mathit{net}}}_{100\text{--}500\text{ ms}}
  + \underbrace{T_{\mathit{wait}}}_{0\text{--}T_e/2}
  + \underbrace{T_{\mathit{bft}}}_{300\text{--}600\text{ ms}}
  + \underbrace{T_{\mathit{confirm}}}_{{\approx}100\text{ ms}}.
\]
Best case: $\approx 1$--$2$~s.\quad High-load case: $\approx 3$--$5$~s.

\subsection{Throughput Analysis}

Reference validator: RTX~4090, 32-core CPU, 10~Gbps NIC.

\begin{itemize}
  \item GPU parallel ZK verify: $\approx 500$~proofs/s (Groth16, BLS12-381).
  \item Batch cap: $M_{\max} = 300$~TX/batch (conservative).
  \item Epoch duration: $T_e = 5$~s.
  \item Throughput: $300 / 5 = \mathbf{60}$~\textbf{TPS} (single committee).
\end{itemize}

BFT message complexity grows as $O(n^2)$; threshold signature aggregation
keeps finalization bandwidth at $O(n)$ (48-byte shares, one aggregated
signature).
Recommended committee size: $n = 100$--$300$.

\subsection{State Growth}

\begin{itemize}
  \item SpentSet: $300 \times 17{,}280 \times 365 \approx 1.9 \times 10^9$
        entries/year; at 32~bytes/leaf $\approx 60$~GB/year full set.
  \item Light client: $\mathsf{SpentSetRoot}$ (32~bytes) +
        non-membership proof ($\approx 1$~KB); trivial.
  \item RSA Accumulator value: constant 256~bytes.
  \item Pruning: entries older than $W$ epochs ($\approx 90$~days) are
        archived; light clients verify against current epoch snapshot.
\end{itemize}

\subsection{Comparison}

\begin{table}[!t]
\centering
\caption{System comparison on key axes.}
\label{tab:compare}
\begin{tabular}{lccccc}
\toprule
\textbf{System} & \textbf{Finality} & \textbf{TPS} & \textbf{Privacy}
  & \textbf{Energy} & \textbf{Ledger} \\
\midrule
Bitcoin  & ${\sim}60$~min & 7   & Weak & High & Yes \\
Ethereum & ${\sim}15$~s   & 15--30 & Weak & Low  & Yes \\
Zcash    & ${\sim}75$~s   & ${\sim}10$ & Full & Low  & Yes \\
Algorand & ${\sim}4.5$~s  & ${\sim}1000$ & Weak & Low  & Yes \\
\textbf{AXIOM} & \textbf{2--5~s} & \textbf{${\sim}60^*$} & \textbf{Full}
  & \textbf{Minimal} & \textbf{No} \\
\bottomrule
\end{tabular}
{\footnotesize ${}^*$ single committee, reference hardware; horizontal
scaling possible.}
\end{table}

\subsection{Implementation Roadmap}

\begin{enumerate}
  \item \textbf{Phase~1} (3--6 mo): Groth16 circuit (\texttt{arkworks-rs}),
        RSA accumulator, BLS TSig.
  \item \textbf{Phase~2} (3 mo): Single-node prototype; SMT SpentSet;
        \textsf{Apply()} state transition; benchmarks.
  \item \textbf{Phase~3} (6 mo): Multi-node BFT; VDF beacon; DKG key
        rotation; network stress test.
  \item \textbf{Phase~4} (3 mo): Tier~0/1 mempool; PoW-lite + stake tickets;
        dynamic fee market.
  \item \textbf{Phase~5} (3 mo): ECVRF sortition; adaptive $\tau$; sybil
        audit.
\end{enumerate}
Total estimated duration: 18--24 months (small team, production-grade target).
